On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-08 Manuscript/reply.tex
Overlaid Plots for Phi and Sigma

The manuscript has been
revised accordingly with the following notable changes:
\jy{Be selective here for ``notable''. I'd not include items like `wording
  clarification'; your could put all the clarifications as one
  item. Keep this list short for the reviewers to have a  
  quick idea about the major changes (e.g., additional simulation studies).}

\begin{enumerate}
\item Added clarifications of rationals for decisions regarding the experimental
design;
\item Reorganization of paragraphs on the Simulation Study, including moving the
Appendix on the Exponential Marginal Distribution Study to the main text;
\item Further discussion of the justification, advantages, and implications of
the Recentered Percentile CI;
\item Clarified wording and additional citations;
\item More detailed xxamination of limitations of study and block bootstrap 
in general
\item An Appendix on simulation study using block size 
$l = \lceil 2n^{1/3} \rceil$
\end{enumerate}

@@

\jy{put the legend on one line.}

\jy{This plot seems fine to me. Could you make it for the other
  parameters too? Then we can make a decision. If we use this, the
  number of figures would be greatly reduced.}

@@

@@

\jy{Are there big differences? We could report the CP CIs in the paper.}

@@

\jy{I'm interested in seeing the figures overlaid as in
  Figure~\ref{fig:mu}.}

>>>>

The manuscript has been
revised accordingly with the following notable changes:
\jy{Be selective here for ``notable''. I'd not include items like `wording
  clarification'; your could put all the clarifications as one
  item. Keep this list short for the reviewers to have a  
  quick idea about the major changes (e.g., additional simulation studies).}
\mc{addressed}

\begin{enumerate}
\item Added clarifications of design and more detail examination of results;
\item Reorganization of paragraphs on the Simulation Study, including moving the
Appendix on the Exponential Marginal Distribution Study to the main text;
\item Further discussion of the justification, advantages, and implications of
the Recentered Percentile CI;
\item An Appendix on simulation study using block size 
$l = \lceil 2n^{1/3} \rceil$
\end{enumerate}

@@

\jy{put the legend on one line.}
\mc{addressed}

\jy{This plot seems fine to me. Could you make it for the other
  parameters too? Then we can make a decision. If we use this, the
  number of figures would be greatly reduced.}
\mc{addressed}

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt_plot_norm_sigma_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\sigma$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt_plot_norm_phi_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\phi$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:mu}
\end{figure}

@@

\jy{Are there big differences? We could report the CP CIs in the paper.}
\mc{I included it in the paper but they do not seem too different}

@@

\jy{I'm interested in seeing the figures overlaid as in
  Figure~\ref{fig:mu}.}
\mc{addressed}
